### 2019-06-08 doc/chapters/trying_verify_checktx.tex
added label

This chapter describes the part of Bitcoin-S needed to verify the No Inflation Property described before.
We are going to create a transaction and show you the relevant parts of the method checkTransaction, where transactions are checked against some properties.
Then, we will see the bug in Bitcoin-S found during this work and its fix.
In the end we find reasons why it was needed for this work to change the verification from the No Inflation Property to the Addition with Zero Property.

>>>>

This chapter describes the part of Bitcoin-S needed to verify the \nameref{property_1} described before.
We are going to create a transaction and show you the relevant parts of the method checkTransaction, where transactions are checked against some properties.
Then, we will see the bug in Bitcoin-S found during this work and its fix.
In the end we see why the \nameref{property_1} needed to be changed to the \nameref{property_2}.
